\chapter{Conclusion}
\label{sec:conclusion}

In conclusion, our project tackled the task of sorting products by both their looks and descriptions. We adopted solid methods, merging cutting-edge Natural Language Processing and Deep Learning strategies to optimize online product sorting.

We split our data into training, checking, and testing groups. This made sure our model was not just well-prepped, but also checked against fair data sets. The CLIP model from OpenAI is used, which was key in helping the system smartly link pictures and words of products.

The key measure we looked at was the weighted F1 score, and it showed us that our model is really good at accurately figuring out product types. The confusion matrix went a step further, showing us that our model can smartly apply what it's learned to brand new products, a fact that was also proven when it was tested on new data from outside our original set.

In the realm of Data Science, we conducted a comprehensive study where we conceptualized, implemented, and evaluated classification models. As discussed in the previous sections of the report, while the achieved performances are deemed satisfactory, we acknowledge that there are numerous avenues for improvement e.g. using other testing strategies to have a smaller gap betweeen our own testing and testing it on through the challenge website.


%Throughout this project, we have expanded our knowledge in the domains of Natural Language Processing (NLP), multi-class and multimodal classification, as well as honed our skills in Deep Learning using different techniques. \\

%Initially, we navigated the Google Colaboratory notebooks for data visualization throughout  different graphs and u-maps as well as our CNN models utilizing Google colab' GPU. Subsequently, we explored the OpenAI tool clip which excels in understanding and connecting vision and language. \\

%In the realm of Data Science, we conducted a comprehensive study where we conceptualized, implemented, and evaluated classification models. As discussed in the previous sections of the report, while the achieved performances are deemed satisfactory, we acknowledge that there are numerous avenues for improvement yet to bed.


